---
title: "danikue.com demo"
author: 'Danielle Kuehler'
output:
  word_document:
    fig_height: 4.5
    fig_width: 6
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 4.5
    fig_width: 6
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
require(readr)
require(stargazer)

trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=TRUE,     # display code as typed
  size="small")   # slightly smaller font for code
```


# Example 1
The following equation explains salaries of CEOs in terms of annual firm sales, return on equity (roe, in percentage form), and return on the firm's stock (ros, in percentage form):

$$
\log(salary)=\beta_0+\beta_1\log(sales) + \beta_2 roe + \beta_3 ros + u
$$

* Using data in "CEO" to estimate this model. Reporting the regression table using `summary`.

```{r}
#Load libraries
library(readxl)
library(knitr)
library(dplyr)
library(ggrepel)
library(readxl)
library(ggplot2)
library(tidyverse)
library(xtable)
library(stargazer)
library(mosaic)

#From files
ceo_data <- read_excel(path = "ceo.xls")
houseprice <- read_excel(path = "houseprice.xls")

Q1_model1 <- lm(formula = log(salary) ~-1 + log(sales) + roe + ros, data=ceo_data)

#Showing regression with data
visreg::visreg(Q1_model1)

```

```{r}
#Regression table report using summary
summary(Q1_model1)
```
* Testing the null hypothesis that ros has no effect on salary using the estimated model.

```{r}
#CEO data
stargazer(Q1_model1, type = "text", header=FALSE)
```

Conclusion: Ros is statistically significant, p<.01, therefore we reject the null hypothesis, and include ros in a final model.

***


# Example 2
The data "Houseprice" are for houses that sold during 1981 in North Andover, Massachusetts. 1981 was the year construction began on a local garbage incinerator

* Evaluating the effects of the incinerator location on housing price
$$
\log(price)=\beta_0+\beta_1\log(dist)+u,
$$
* where `price` is housing price in dollars and `dist` is the distance from the house to the incinerator measured in feet.

Prediction: We expect $\beta_1$ to be positive, because the further the house is from the incinerator, the higher the price.

```{r}
library(readxl)
houseprice <- read_excel(path = "houseprice.xls", sheet=1, col_names = TRUE)
Q2_model1 <- lm(formula = log(price) ~ log(dist), data = houseprice)

#Model for houseprice and distance from incinerator
visreg::visreg(Q2_model1)

#Data on price and dist
stargazer(Q2_model1, type = "text", ci = TRUE, ci.level = .9)
```

* Adding variables $\log(intst)$, $\log(area)$, $\log(land)$, $rooms$, $baths$ and $age$ where `intst` is distance from the home to the interstate, `area` is square footageof the house, `land` is the lot size in square feet, `rooms` is total number of rooms, `baths` is number of bathrooms and `age` is age of the house in years.


```{r}
#Adding variables
Q2_model2 <- lm(formula = log(price) ~-1 + log(dist) + log(intst) + log(area) + log(land) + rooms + baths + age, data = houseprice)
#Data model
visreg::visreg(Q2_model2)
```
```{r}
#Data summary
library(stargazer)
stargazer(Q2_model1, Q2_model2,type="text", header = FALSE, ci = TRUE, ci.level = 0.9)
```
Conclusion: Distance from the incinerator largely effects the price of the house, the further the house is the higher the price, and it is statistically significant at the 90% confidence interval, p<0.01